Target Markdown

### 2022-05-12 _targets.Rmd
pipline iteration done

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv")),
              format = "qs"),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids), 
              format = "qs")

@@

   tar_target(topic_model, 
              make_topic_model(all_pubs),
               format = "qs")

@@

    tar_target(edgelist,
               make_edgelist(one_author),
                format = "qs"),
    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE) )

@@

    tar_target(eigen_centr,
               calc_eigen_centr(graph), 
               format = "qs")

@@

    tar_target(clustering,
               calc_clustering(graph), 
               format = "qs")

@@

    tar_target(ind_pubs,
               calc_ind_pubs(one_author), 
               format = "qs")

@@

    tar_target(ind_topics,
               calc_ind_topics(topic_model, two_authors), 
               format = "qs")

@@

    tar_target(ind_topics_cs,
               calc_cos_sim(topic_model, two_authors), 
               format = "qs")

@@

```{r}

>>>>

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

@@

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs),
                format = "qs") #,
   # --> fce find k 
   # tar_target(topic_model,
   #            make_topic_model(topic_model_input),
   #             format = "qs")

@@

    tar_target(edgelist,
               make_edgelist(one_author),
                format = "qs", pattern = map(one_author), iteration = "list"),
    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")

@@

    tar_target(eigen_centr,
               calc_eigen_centr(graph, ids_complete, one_author, db_path),
               format = "qs", pattern = map(graph, one_author), iteration = "list")

@@

    # tar_target(clustering,
    #            calc_clustering(graph), 
    #            format = "qs")
    # 
)

@@

    # tar_target(ind_pubs,
    #            calc_ind_pubs(one_author), 
    #            format = "qs")
    # 
)

@@

    # tar_target(ind_topics,
    #            calc_ind_topics(topic_model, two_authors), 
    #            format = "qs")

@@

    # tar_target(ind_topics_cs,
    #            calc_cos_sim(topic_model, two_authors), 
    #            format = "qs")
    # 
)

@@

```{targets final}

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL),
               format = "qs")
